Technical Report

### 2024-02-26 Reports/tech_report1.tex
update report

@@

\begin{itemize}
	\item\emph{Experiments Id}: 022200102024

@@

>>>>

\subsection{Find best open ReLU for layer 5 for normal 5x100, new pure y-constraints}

This experiment is to find the best open ReLU number for layer 5 normal 5x100 with new pure-y constraints constraints.

The running code's file name is \verb*|DiamondLipschitz_V0p3_test.py|. And the partial output file name is \verb*|DL_V0p3_layer5_find_best_number.txt|.  It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 5 with different open ReLU numbers.

\begin{itemize}
	\item\emph{Experiments Id}: 022100202024

	\item\emph{Open $\ReLU$ number:} Open 25,28,31, 34, 37 ReLU nodes for each node.

	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_21_13_58_49.b|; this file stores all alpha beta gamma of nodes of all layers for the same network,and the data of gamma of layer 3 using the latest method. 
\end{itemize}

Not completed. So here is the summary of the partial results.

\begin{itemize}
	\item \emph{Log:} \verb*|DL_V0p3_layer5_find_best_number.txt|.

	\item \emph{Key results:}  $\gamma$ for different open numbers are

	Open 25 
	Bound: 0.8382390973953313 , Solution: 0.8321314445556547 , Time: 306.77194131612777 2335.830235481262

	Open 28 
	Bound: 0.8147201914056824 , Solution: 0.8054690328829098 , Time: 1176.2175419330597 7200.522756814957

	Open 31 
	Bound: 0.7963056225858687 , Solution: 0.7818023933666046 , Time: 3502.1967465043067 7200.723284482956

	Open 34 
	Bound: 0.7945120282557274 , Solution: 0.7582789017028382 , Time: 5760.061596000194 7200.779401540756

	Open 37 (not finished) 
	Bound: 0.8022403621011988 , Solution: 0.7360574057164293 , Time: 4956.505218315125 7200.661721229553

	It seems that 34 is the best. In following experiments, we use open 33 node.

@@

\begin{itemize}
	\item\emph{Experiments Id}: 022200302024

@@

\section{February 22-25 experiments}

\subsection{Find best open ReLU for layer 5 for normal 5x100, new pure y-constraints}

This experiment is to find the best open ReLU number for layer 7 normal 5x100 with new pure-y constraints constraints.

The running code's file name is \verb*|DiamondLipschitz_V0p3_test.py|. And the partial output file name is \verb*|DL_V0p3_layer7_find_Best_open_number.txt,DL_V0p3_layer7_find_Best_open_number2.txt,DL_V0p3_layer7_find_Best_open_number3.txt,DL_V0p3_layer7_find_Best_open_number4.txt|.  It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with different open ReLU numbers.

\begin{itemize}
	\item\emph{Experiments Id}: 022500102024

	\item\emph{Open $\ReLU$ number:} Open 30, 33, $\cdots$, 72 ReLU nodes for each node (in 3 tests).

	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_02_23_09_28_54.b|; this file stores all alpha beta gamma of nodes of all layers for the same network,and the data of gamma of layer 5 using the latest method. 
\end{itemize}

Not completed. So here is the summary of the partial results.

\begin{itemize}
	\item \emph{Log:} \verb*|DL_V0p3_layer7_find_Best_open_number.txt,DL_V0p3_layer7_find_Best_open_number2.txt,DL_V0p3_layer7_find_Best_open_number3.txt,DL_V0p3_layer7_find_Best_open_number4.txt|.

	\item \emph{Key results:}  $\gamma$ for different open numbers are

	It seems that 34 is the best. In following experiments, we use open 33 node.
